Autonomous Oceanographic Data Collection using Excursion Sets of Vector-valued Gaussian Random Fields

### 2020-06-21 main_new.tex
Sect 3 revised in main_new.tex.

The spatial-statistical design criterion building on random sets is
relevant in our setting with different water properties. 
We show
mathematical generality beyond the expected integrated Bernoulli variance, for instance that of volume uncertainties which is possibly more relevant, but requires more computational resources.
Such criteria could be particularly useful in other oceanographic settings of algal-blooms, anoxic
zones or open water fronts \cite{costa19}.
Of course, other criteria
are also relevant for instance, hybrid or multi-attribute criteria
that could balance goals of exploration and exploitation in this
situation. Equally, such techniques have significant use cases in
downstream decision-making, with policy makers and regulators who need
to make difficult decisions related to fish farming or other marine
resource operations, and value of information analysis
\citep{Eidsvik:15} could be used to evaluate whether
information is likely to result in improved decision-making.
We also foresee opportunities related to more nuanced design of expfor multivariate processes using the notion of generalized locations.

>>>>

The spatial-statistical design criterion building on random sets is
relevant in our setting with different water properties. 
We show
mathematical generality beyond the expected integrated Bernoulli variance, for instance that of volume uncertainties which is possibly more relevant, but requires more computational resources.
Such criteria could be particularly useful in other oceanographic settings of algal-blooms, anoxic
zones or open water fronts \cite{costa19}.
Of course, other criteria
are also relevant for instance, hybrid or multi-attribute criteria
that could balance goals of exploration and exploitation in this
situation. Equally, such techniques have significant use cases in
downstream decision-making, with policy makers and regulators who need
to make difficult decisions related to fish farming or other marine
resource operations, and value of information analysis
\citep{Eidsvik:15} could be used to evaluate whether
information is likely to result in improved decision-making.
We also foresee opportunities related to design of experiments for multivariate processes using our notion of generalized locations. For instance, this is likely to be useful for internet-of-things applications or computer experiments context, where some observations or evaluations are rather inexpensive, while others are much more costly and must only be done when they are really valuable.
